# Correlation Coefficient 

The word correlation is used widely in our daily conversations.  It means many things depending on the context.  In statistic,  we have a definite meaning and a limitation to this word.  It primarily depends on the datatype.  For example, it is a reasonable question to ask that whether there is a correlation between a person's skin color and their income.  But it is hard to quantify this because race is a categorical variable and income is numerical. In statistics, when we talk about correlation, we generally mean the correlation between two numerical variables such as height and weight.

```{example}
Suppose you are interested in the correlation between amount of sleep and GPA.
```

\


```{r echo=FALSE, message=FALSE, warning=FALSE}
load('./data_for_chapters/corrplot.rda')
corr_plot$data |>
  ggplot() +
  aes(x = x, y = y) +
  geom_point() +
  labs(x = 'Amount of sleep in hours',
       y = 'GPA',
       title = 'Sleeping Increases your GPA?')
```



```{r message=FALSE, warning=FALSE}
corr_plot$data |>
  summarize('correlation' = cor(x, y))
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
wage_data %>%
  ggplot() +
  aes( x = age, y = wage) +
  geom_point() +
  theme_economist() +
  labs(title = 'What is the Correlation?',
       x = 'Age',
       y = 'Weekly Wage (in 2009)')
```

```{r message=FALSE, warning=FALSE}
wage_data |>
  summarize('correlation'= cor(wage, age))
```

`r colorize("TWO variables", "red")`
`r resize_text(x= 'The sample correlation coefficient is defined as:', size = 20)`





$$ \frac{\sum_{i=1}^n (x_i - \bar x)(y_i - \bar y)}{SD_x SD_y} $$



